Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-27 talk/icooolps2011/paper.tex
- a title - shorten a sentence

\title{XXX in a Tracing JIT Compiler for Efficient Dynamic Languages}

@@

Conceptually the significant speed-ups that can be achieved with
dynamic compilation depends on feeding into compilation and exploiting
values observed at runtime that are in practice mostly constant (XXX or should we say slow varying), and
in structuring implementation code and data structures such that more
of such values are at hand. The hints that we present allow exactly to implement such feedback and exploitation in a meta-tracing context.

Concretely these hints are used to control how the optimizer of the
tracing JIT can improve the traces of the object model. More
specifically, these hints influence the constant folding
optimization. The first hint make it possible to turn arbitrary
variables in the trace into constant. The
second hint allows the definition of additional foldable operations.

>>>>

\title{Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages}

@@

Conceptually the significant speed-ups that can be achieved with
dynamic compilation depend on feeding into compilation and exploiting
values observed at runtime that are slow-varying in practice. To exploit the
runtime feedback, the implementation code and data structures need to be
structured so that many such values are at hand. The hints that we present allow
exactly to implement such feedback and exploitation in a meta-tracing context.

Concretely these hints are used to control how the optimizer of the
tracing JIT can improve the traces of the object model. More
specifically, these hints influence the constant folding
optimization. The first hint makes it possible to turn arbitrary
variables in the trace into constant by feeding back runtime values. The
second hint allows the definition of additional foldable operations.
